Supporting Information:\\Black-swan events in animal populations

### 2016-05-26 text/ms.tex
Update cover page

\textbf{Title: Black-swan events in animal populations}

\textbf{Authors}: Sean C. Anderson\textsuperscript{1,2*}, Trevor A.
Branch\textsuperscript{3}, Andrew B. Cooper\textsuperscript{2}, Nicholas K.
Dulvy\textsuperscript{1}

@@

%125

\textbf{Abstract}: Black swans are improbable events that nonetheless
occur---often with profound consequences. While physical extremes, such as
monsoons and heat waves, are widely studied and increasing in magnitude and
frequency, it remains unclear the extent to which ecological population numbers
buffer or suffer from such extremes. Here we estimate the frequency and
direction of black-swan events in \NPops\ animal populations, finding strong
evidence for their occurrence in \(\sim\)\overallBasePerc \% of populations.
Black-swan events occur most frequently for birds (\birdPH \%), mammals
(\mammalsPH \%), and insects (\insectsPH \%), and manifest primarily as
population die-offs and crashes (\percBSDown \%) driven by extrinsic
perturbations from climate variability. Thus, ignoring black-swan events will
underestimate extinction risk. Our results demonstrate the importance of both
modeling heavy-tailed downward events in populations, and developing
conservation strategies that are robust to future increases in climate
extremes.

>>>>

\section{Black-swan events in animal populations}

Sean C. Anderson\textsuperscript{1,2*}, Trevor A.
Branch\textsuperscript{3}, Andrew B. Cooper\textsuperscript{2}, Nicholas K.
Dulvy\textsuperscript{1}

@@

Short title: Black-swan events in animal populations

Keywords:
Bayesian,
black swans,
die-offs,
ecological surprises,
heavy tails,
Gompertz,
mass mortality,
population dynamics,
risk,
Student t

Words in abstract: TOdO

Words in main text: todo

Number of references: todo

Number of figures: 4

Number of tables: 0

\newpage
%125 now is 150

\section{Abstract}
occur---often with profound consequences. While physical extremes, such as
monsoons and heat waves, are widely studied and increasing in magnitude and
frequency, it remains unclear the extent to which ecological population numbers
buffer or suffer from such extremes. Here we estimate the frequency and
direction of black-swan events in \NPops\ animal populations, finding strong
evidence for their occurrence in \(\sim\)\overallBasePerc \% of populations.
Black-swan events occur most frequently for birds (\birdPH \%), mammals
(\mammalsPH \%), and insects (\insectsPH \%), and manifest primarily as
population die-offs and crashes (\percBSDown \%) driven by extrinsic
perturbations from climate variability. Thus, ignoring black-swan events will
underestimate extinction risk. Our results demonstrate the importance of both
modeling heavy-tailed downward events in populations, and developing
conservation strategies that are robust to future increases in climate
extremes.
